---
title: "Code for V2_analysis"
output: html_notebook
---

Loading libraries
```{r}
library(tidyverse)
library(tidyr)
library(viridis)
library(viridisLite)
library(markdown)
library(ggplot2)
library(dplyr)
library(lme4)
library(lmerTest)
library(effects)
library(broom.mixed)
```

## logit2prob function
```{r}
# logit2prob function that converts log odds to probabilities
logit2prob <- function(logit){
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
}
```

# Checking class and setting contrast codes
Korpus_dec was the name of the dataset.

```{r}
Korpus_dec$L1_V2 <- as.factor(Korpus_dec$L1_V2)
Korpus_dec$Kendskab_V2 <- as.factor(Korpus_dec$Kendskab_V2)
Korpus_dec$subjekt_et_eller_flere_ord <- as.factor(Korpus_dec$subjekt_et_eller_flere_ord)
Korpus_dec$verbal_sammensat <- as.factor(Korpus_dec$verbal_sammensat)
Korpus_dec$overtype <- as.factor(Korpus_dec$overtype)

class(Korpus_dec$ord_i_forfelt)
class(Korpus_dec$L1_V2)
class(Korpus_dec$Kendskab_V2)
class(Korpus_dec$subjekt_et_eller_flere_ord)
class(Korpus_dec$verbal_sammensat)

levels(Korpus_dec$L1_V2)
levels(Korpus_dec$Kendskab_V2)
levels(Korpus_dec$subjekt_et_eller_flere_ord)
levels(Korpus_dec$verbal_sammensat)

contrasts(Korpus_dec$L1_V2) <- c(-0.5,0.5)
contrasts(Korpus_dec$Kendskab_V2) <- c(0.5,-0.5)
contrasts(Korpus_dec$subjekt_et_eller_flere_ord) <- c(-0.5,0.5)
contrasts(Korpus_dec$verbal_sammensat) <- c(0.5,-0.5)
```

# Creating subset without V2 learners
```{r}
subset_uden_V2_learners <- subset(Korpus_dec, L1_V2 == "ikke_V2")
```

# Model
```{r}
m1 <- glmer (overtype ~ ord_i_forfelt + subjekt_et_eller_flere_ord + verbal_sammensat + CEFR_num + L1_V2 + (1|deltager), data=Korpus_dec, family = binomial)
summary(m1)
```

# Calculating probabilities from estimates using logit2probe function
```{r}
# converting the intercept
logit2prob(1.56686) 
logit2prob(1.56686+0.49374) 
logit2prob(1.56686+2.38632) 
```

# Scatterplot 

```{r}
theme_set(theme_bw())
plot1 <- ggplot(Korpus_dec, aes(x=CEFR_num, y=overtype, shape=L1_V2, color=L1_V2)) + geom_point(position="jitter")
plot1
```


# Model without V2 learners 

```{r}
m2 <- glmer (overtype ~ ord_i_forfelt + subjekt_et_eller_flere_ord + verbal_sammensat + Kendskab_V2 + CEFR_num + (1|deltager), data=subset_uden_V2_learners, family = binomial)
summary(m2)
```


# Calculating probabilities from estimates using logit2probe function
```{r}
# converting the intercept
logit2prob(0.47703) 
logit2prob(0.47703+0.55027) 

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
